Dark Control:\\ A Unified Account of Default Mode Function\\ by Control Theory and Reinforcement Learning

### 2017-04-21 paper/paper.tex
a small pass on manuscript

\begin{mdframed}
\begin{definition*}
% \textbf{XXX Danilo: Is there a definition 2 somewhere?}
Mathematically, a POMDP is simply a quintuplet $(\mathcal S, \mathcal A, r, p, \mu)$ where
\begin{itemize}
\item $\mathcal S$ is the set of states, such as $\mathcal S = \{\text{happy}, \text{sad}\}$.
\item $p : \mathcal S \times \mathcal A \times \mathcal S \rightarrow [0, 1],\; (s,a,s') \mapsto p(s'|s,a)$,
  the probability of moving to state $s'$ if action $a$ is taken from state $s$. In addition, one requires that such
  transitions be Markovian. Consequently, the future states are independent of past states and only depend on the present.
\item $\mathcal A$ is the set of actions, such as $\mathcal A = \{\text{read}, \text{run},
  \text{laugh}, \text{sympathize}, \text{empathize}\}.$
\item $r : \mathcal S \times \mathcal A \rightarrow \mathbb R$ is the \textit{reward function},
  so that $r(s, a)$ is the instant reward for taking action $a$ in state $s$.
\item $\mu: \mathcal S \rightarrow [0, 1]$ is the prior probability on the states so that
  $\mu(s)$ is the probability that the environment starts off in state $s$.
\end{itemize}

% \begin{remark}
%   Given a system $(\mathcal S, \mathcal A, r, p, \mu)$ satisfying all the axioms for an MDP
%   except the Markov property, we can always transform it into an MDP by considering a compounded
%   version of the states
%   $$S_t \leftarrow (S_0,A_0,R_0,S_1,A_1,S_2\ldots,S_t,A_{t-1},R_{t-1},S_{t})$$ made of the system's
%   history up to an including time $t$.
% \end{remark}
\end{definition*}
\end{mdframed}

>>>>

\begin{definition*}
Mathematically, a POMDP is simply a quintuplet $(\mathcal S, \mathcal A, r, p, \mu)$ where
\begin{itemize}
\item $\mathcal S$ is the set of states, such as $\mathcal S = \{\text{happy}, \text{sad}\}$.
\item $p : \mathcal S \times \mathcal A \times \mathcal S \rightarrow [0, 1],\; (s,a,s') \mapsto p(s'|s,a)$,
  the probability of moving to state $s'$ if action $a$ is taken from state $s$. In addition, one requires that such
  transitions be Markovian. Consequently, the future states are independent of past states and only depend on the present.
\item $\mathcal A$ is the set of actions, such as $\mathcal A = \{\text{read}, \text{run},
  \text{laugh}, \text{sympathize}, \text{empathize}\}.$
\item $r : \mathcal S \times \mathcal A \rightarrow \mathbb R$ is the \textit{reward function},
  so that $r(s, a)$ is the instant reward for taking action $a$ in state $s$.
\item $\mu: \mathcal S \rightarrow [0, 1]$ is the prior probability on the states so that
  $\mu(s)$ is the probability that the environment starts off in state $s$.
\end{itemize}

\end{definition*}

\begin{remark}
  Given a system $(\mathcal S, \mathcal A, r, p, \mu)$ satisfying all the axioms for an MDP
  except the Markov property, we can always transform it into an MDP by considering a compounded
  version of the states
  $$S_t \leftarrow (S_0,A_0,R_0,S_1,A_1,S_2\ldots,S_t,A_{t-1},R_{t-1},S_{t})$$ made of the system's
  history up to an including time $t$.
\end{remark}
